%
% CMPT 473: Software Quality Assurance - A Course Overview
% Section: Input Space Partitioning
%
% Author: Jeffrey Leung
%

\section{Input Space Partitioning}
	\label{sec:input-space-partitioning}
\begin{easylist}

& \textbf{Input Space Partitioning:} Division of potential inputs into classes where each input in a class should yield identical output

& \textbf{Input Domain Model:} Description of possible test inputs through discrete partitions which are disjoint and cover the entire domain
	&& \textbf{Interface-based approach:} Choosing inputs for a domain model based on parameters and domains
	&& \textbf{Functionality/requirements-based approach:} Choosing inputs for a domain model based on behaviours or functionality in the specification

& Process:
	&& Identify and isolate the component under test
	&& Identify inputs
		&&& Possible values to be partitioned:
			&&& Parameters and inputs
			&&&& Object state
			&&&& Global state
			&&&& File contents
	&& Identify characteristics of each input to divide into possible values
	&& Identify constraints
		&&& Characteristics to consider:
			&&&& Preconditions and postconditions
			&&&& Relationships to special values
			&&&& Relationships between variables
	&& Select representative values from an input block, including:
			&&&& Expected/valid values
			&&&& Special values
			&&&& Invalid values
			&&&& Boundary values

& E.g. Given a command to FIND instances of a PATTERN in a FILE:
	&& The component is the FIND command
	&& The parameters are the pattern to search for, the filename, and the file contents
	&& The characteristics include:
	 	&&& Is the pattern empty?
		&&& Is the length of the pattern contents less than, the same as, or greater than the length of the longest line in the file?
		&&& Does the pattern have quotation marks enclosing it?
		&&& Are ther escaped quotation marks in the pattern?
		&&& Is the filename empty?
		&&& Does the file exist?
		&&& Is the file a directory?
		&&& Is the file blank?
		&&& Does the file have a blank line?
		&&& Is there a line in the file matching the pattern multiple times?

\end{easylist}
\subsection{Test Combination Strategies}
	\label{subsec:input-space-partitioning:test-combination-strategies}
\begin{easylist}

& * means any value is valid

& \textbf{Each Choice:} From each block, use at least one value in at least one test
	&& Size: Largest domain
	&& Does not cover many possible conflicting states
	&& E.g. Given inputs A/B/C and 1/2, an adequate set of tests are:
		&&& A 1
		&&& B 2
		&&& C *

& \textbf{Pair Wise:} From each block, choose 1 value and test it at least once with every value from every other block
	&& Size (lower bound): $\geq$ the product of the domain sizes of the two largest partitions
	&& E.g. Given inputs A/B/C, 1/2, and X/Y, an adequate set of tests are:
		&&& A 1 X
		&&& A 2 Y
		&&& B 1 Y
		&&& B 2 X
		&&& C 1 *
		&&& C 2 *

& \textbf{T-Wise:} From each block, test 1 value for each group of $T$ characteristics
	&& Size: $\geq$ product of the $T$ largest domain partitionings

& \textbf{Base Choice:} Create a base test and create tests by changing only a single value and fixing the others
	&& Size: 1 base test plus one for each other unselected block
	&& Base case must be a valid positive test

& Hierarchy of test type satisfaction:
	&& All combinations includes all T-Wise tests and Multiple Base Choice testing
		&&& T-Wise testing includes all Pair-Wise tests
			&&&& Pair-Wise tests includes all Each Choice tests
		&&& Multiple Base Choice testing includes all Base Choice tests
			&&&& Base Choice tests includes all Each Choice tests

\end{easylist}
\clearpage
