%
% BUS 361: Project Management - A Course Overview
% Section: Flashcard Questions
%
% Author: Jeffrey Leung
%

\section{Flashcard Questions}
	\label{sec:flashcard-questions}
\begin{easylist}

& What does PMBOK stand for?
	&& Project Management Body of Knowledge
& What are the 10 PMBOK knowledge areas?
	&& Scope, time, cost, quality, human resources, communications, risk, procurement, stakeholder, integration
& What is the difference between projects and operations?
	&& Project: Unique, temporary, uncertain
	&& Operation: Repeated, ongoing, with known performance
& What is the greatest threat to project success?
	&& Communication failure
& What is a project?
	&& Temporary venture to create a unique result
& What are the 5 process groups in the project life cycle?
	&& Initialization, planning, execution, monitoring/controlling, closing
& What is a stakeholder?
	&& An entity which affects or is affected by the project
& Quality of results is a balance of:
	&& Scope, cost, schedule
& What is the difference between duration and effort?
	&& Duration: The length of time spent on an activity including breaks and other activities
	&& Effort: The length of time spent on an activity not including breaks and other activities
& What three values does Three Point Estimation average?
	&& Most likely, pessimistic, and optimistic estimates
& What is the difference between free float and total float?
	&& Free float: The amount of time an activity can be delayed without affecting future activities
	&& Total float: The amount of time an activity can be delayed without affecting project completion date
& What are the steps of risk management?
	&& Identification, analysis, response, monitoring
& What are common responses to risk?
	&& Avoidance, mitigation, transfer, acceptance
& What does RACI stand for?
	&& Responsible, Accountable, Consulted, Informed
& What characteristics does Earned Value analyze?
	&& Technical, schedule, cost
& What is the equation for Earned Value (EV)?
	&& $EV = \textrm{Cost at completion} \times \textrm{Percentage completed}$
& What is the equation for Cost Variance (CV)?
	&& $CV = EV - AC$ (actual cost so far)
& What is the equation for Cost Performance Index (CPI)?
	&& $CPI = \frac{EV}{AC}$ (actual cost so far)
& What is the equation for Schedule Performance Index (SPI)?
	&& $SPI = \frac{EV}{PV}$
& What are Tuckman's 5 Team Development Stages?
	&& Forming, Storming, Norming, Performing, Adjourning
& Of task, process, and relationship conflict, which are the most likely to be functional conflict?
	&& Task or process
& What is the best way to capture lessons learned?
	&& Documenting lessons as they occur
	
\end{easylist}
\clearpage